Parallel Deduplication with Batch Scheduling for Collocated Virtual Machine Backup in the Cloud

### 2014-01-07 batchdedup/background.tex
added support for our general purpose approach to backround. added initial simulation approach description to eval.

>>>>

Further, System admistrators may wish to adjust the balance between resource 
usage for backup and the time spent performing backups. There may be a small
backup window (e.g. 2 hours) to complete the backups each night, but the backup
should also minimize impact on VMs running during that time. Other studies have
shown, for example, that the cost of Copy on Write (CoW) during daily backups
can be as much as 8\% of the total data size \cite{EMCIncrementalDataChanges}.

### 2014-01-07 batchdedup/eval.tex
added support for our general purpose approach to backround. added initial simulation approach description to eval.

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Total Network Memory Buffer (MB)},
		ylabel={Backup Time},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north west
		]
                \addplot table[x=mpibufmem,y=totaltime] {figures/mpibufmem.txt};
                %\legend{Total Backup Time};
		\end{axis}
	\end{tikzpicture}
  \caption{Backup time for verying amounts of memory allocated to network communication. Other Settings: 10 Machines, 5x40GB VMs per machine, write buffer 6.25MB, Read Buffer 128KB}
  \label{fig:mpibuf-mem}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Rounds},
		ylabel={Throughput (GB/s)},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north west
		]
                \addplot table[x=rounds,y=throughput] {figures/sim_full.txt};
                %\legend{Total Backup Time};
		\end{axis}
	\end{tikzpicture}
  \caption{simulated results for average throughput for individual VMs in 100 node cluster.}
  \label{fig:mpibuf-mem}
\end{figure}
\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Rounds},
		ylabel={Average Backup Time (min)},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north west
		]
                \addplot table[x=rounds,y expr=(\thisrow{avgbackuptime})/60] {figures/sim_full.txt};
                %\legend{Total Backup Time};
		\end{axis}
	\end{tikzpicture}
  \caption{simulated results for average vm backup time for individual VMs in 100 node cluster.}
  \label{fig:mpibuf-mem}
\end{figure}

@@

@@

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Rounds},
		ylabel={Average Backup Time (s)},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
                %legend pos=north west
		]
                \addplot table[x=Rounds,y=DBP2avgbackup] {figures/packing_comparison.txt};
                \addplot table[x=Rounds,y=BPLavgbackup] {figures/packing_comparison.txt};
                \legend{DBP2, BPL};
		\end{axis}
	\end{tikzpicture}
  \caption{Average Backup Time for DBP2 and BPL}
  \label{fig:avgbackup-comparison}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Total Network Memory Buffer (MB)},
		ylabel={Backup Time (hrs)},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north west
		]
                \addplot table[x=mpibufmem,y expr=(\thisrow{totaltime}/3600)] {figures/mpibufmem.txt};
                %\legend{Total Backup Time};
		\end{axis}
	\end{tikzpicture}
  \caption{Backup time for verying amounts of memory allocated to network communication. Other Settings: 10 Machines, 5x40GB VMs per machine, write buffer 6.25MB, Read Buffer 128KB}
  \label{fig:mpibuf-mem}
\end{figure}

@@

\subsection{Simulated Algorithm Comparison}

Based on results from out trace-driven study, we also compare algorithms using
the amount of data transferred over the network, written to disk, and read from
disk in each stage. From this simple performance model, we can compare
different scheduling heuristics and weights and choose the most appropriate
algorithm for a set of requirements. Our simulation uses VM size distributions
from production clusters to evaluate the scheduling algorithms across several
clusters. we discuss the size distributions in section \ref{??}.

@@

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Rounds},
		ylabel={Average Backup Time (hrs)},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
                %legend pos=north west
		]
                \addplot table[x=Rounds,y expr=(\thisrow{DBP2avgbackup}/3600)] {figures/packing_comparison.txt};
                \addplot table[x=Rounds,y expr=(\thisrow{BPLavgbackup}/3600)] {figures/packing_comparison.txt};
                \legend{DBP2, BPL};
		\end{axis}
	\end{tikzpicture}
  \caption{Average Backup Time for DBP2 and BPL}
  \label{fig:avgbackup-comparison}
\end{figure}
